Kung Faux Pandas \\ \large Alternative Facts for Privacy Preservation

### 2018-05-10 paper/seth.tex
Auto Update from local Sharelatex

>>>>

 \section{Reproducibility}
 %Good discussion of what reproducibilty vs replicability means
 %http://languagelog.ldc.upenn.edu/nll/?p=21956
 To clarify what we mean by reproducibility in machine learning, a brief discussion of what the term reproducibility
 Over the past 15 years or so, there has been some significant papers clarifying the definition and importance of reproducibility, along with the closely related term replicability. Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experi- ment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}. One early influential paper on the topic of reproducibility in scientifici computing by Schwab details key factors in reproducbility as: having data, input parameters, documenation, software code, and an environment capable of running the provided software code \cite{schwab_making_2000}.
